Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2014-07-24 draft.tex
Fix typo in the abstract

\begin{abstract}
In this letter we study how to obtain a set of angular observables
$\{P_i\}$ that arise in a generic multi-body process without the need
to carry out a likelihood fit of an angular distribution to the
measured events. Instead, we present a method that only relies on
orthogonality of angular functions, and estimation of integrals
by means of Monte Carlo techniques. Beyond providing estimators
for central values and uncertainties, we provide means to determine
the correlation between all angular observables. We show that detector
acceptance effects can be accounted for in the analysis.
\end{abstract}

>>>>

\begin{abstract}
In this letter we study how to obtain a set of angular observables
$\{S_i\}$ that arise in a generic multi-body process without the need
to carry out a likelihood fit of an angular distribution to the
measured events. Instead, we present a method that only relies on
orthogonality of angular functions, and estimation of integrals
by means of Monte Carlo techniques. Beyond providing estimators
for central values and uncertainties, we provide means to determine
the correlation between all angular observables. We show that detector
acceptance effects can be accounted for in the analysis.
\end{abstract}
